---
title: "DM_analysis"
author: "Anita and Anna"
date: "1/3/2020"
output: html_document
---

# Set up
```{r}
pacman::p_load(tidyverse, viridis)
```


# Data preparation

*Respondent data*
```{r}
original_df <-read.csv("dataset.csv", sep = )

complete <- original_df %>% 
  filter(original_df$stato_4 == 1)

complete$gender = ifelse(complete$gender == 1, "Female", "Male")

complete %>% group_by(gender) %>% summarise(n())

test <- complete %>% 
  select(responde, difftime, age, gender, rating_m, volume_m, content_, q1_a_or_:q20_b)

test_reshaped <- gather(test, Question_idS, Response, q1_a_or_:q20_b, factor_key = TRUE) 
test_reshaped2 <- test_reshaped %>% drop_na(Response)

test_reshaped3 <- test_reshaped2 %>% 
  mutate(Question_type = ifelse(grepl("or", Question_idS),"volume_valence_dilemma", "distribution"))

volume_valence <- test_reshaped3 %>% 
  filter(Question_type == "volume_valence_dilemma")

distribution <- test_reshaped3 %>% 
  filter(Question_type == "distribution")

#write_csv(volume_valence, "volume_valence.csv")
#write_csv(distribution, "distribution.csv")
```


*Question data* and merging with dataframes
```{r}
question_df <-read.csv("nodist.csv")
question_df$Question_ID <-  as.character(question_df$Question_ID)
question_df$X <- NULL

vvfull <- volume_valence %>% 
  mutate(Question_ID = gsub("[^0-9]", "", Question_idS)) %>% 
  inner_join(question_df, by = "Question_ID")

vvfull$order <- NULL
vvfull$Response <- ifelse(vvfull$Response == 1, "A", "B")
vvfull$Response <- as.factor(vvfull$Response)
vvfull$Question_type <-  NULL
vvfull_test <- vvfull %>% 
  mutate(Choice = ifelse((vvfull$order == "2 is A" & vvfull$Response == "B")|(vvfull$order == "1 is A" & vvfull$Response == "A"), "1", "2"))

vvfull_test %>% group_by(Choice) %>% summarise(n())

vvfull_test$rating_m <- as.factor(as.character(vvfull_test$rating_m))
levels(vvfull_test$rating_m) <- c("Not at all","a small extent","a large extent", "depends")
vvfull_test$volume_m <- as.factor(as.character(vvfull_test$volume_m))
levels(vvfull_test$volume_m) <- c("a small extent","a large extent", "depends")
vvfull_test$content_ <- as.factor(as.character(vvfull_test$content_))
levels(vvfull_test$content_) <- c("Not at all","a small extent","a large extent", "depends")

vvfull_test$participant_ID <-as.factor(as.numeric(as.factor(vvfull_test$responde)))

vvfull_final <- vvfull_test %>% 
  mutate(chosen_valence = ifelse(Choice == 1, valence_1, valence_2),
         chosen_volume = ifelse(Choice == 1, volume_1, volume_2),
         not_chosen_valence = ifelse(Choice == 1, valence_2, valence_1),
         not_chosen_volume= ifelse(Choice == 1, volume_2, volume_1)) %>% 
  mutate(valence_gain = chosen_valence - not_chosen_valence,
         volume_gain = chosen_volume - not_chosen_volume) %>% 
  select(Participant_ID = participant_ID, time = difftime, age, gender, rating_opinion = rating_m, volume_opinion = volume_m, content_opinion = content_, Question_ID = Question_ID, chosen_valence, chosen_volume, not_chosen_valence, not_chosen_volume, valence_gain, volume_gain )


write_csv(vvfull_final, "almost_final_nodist.csv")

distribution_too <- distribution %>% 
  mutate(chosen_dist = ifelse(Response == 1, "larger_range", "smaller_range"),
         Question_ID = gsub("[^0-9]", "", Question_idS),
         Participant_ID = as.factor(as.numeric(as.factor(distribution$responde)))) %>%
  select(Participant_ID, Question_ID, chosen_dist) %>% 
  inner_join(vvfull_final, by = c("Participant_ID", "Question_ID")) %>% 
  select(Participant_ID, Question_ID, time, everything() )

distribution_too %>% group_by(chosen_dist) %>% summarise(n())

write_csv(distribution_too, "final_purchasing_decisions.csv")
```
Logic:
if order = "2 is A" and Response = A -> Choice  = 2
if order = "2 is A" and Response = B -> Choice = 1
if order = "1 is A" and Response = A -> Choice = 1
if order = "1 is A" and Response = B -> Choice = 2


# Data visualization
```{r}
df <-  distribution_too

df <- df %>% 
  mutate(volume_diff = as.factor(abs(volume_gain)),
         valence_diff = as.factor(round(abs(valence_gain), 1)),
         preference = ifelse(valence_gain > 0, "valence", "volume"))




######### Data distributions

ggplot(df, aes(valence_gain, color = "purple"))+
  geom_density( aes(fill = preference, alpha = 0.5), position = "dodge") +
  theme_classic()+
  geom_vline(data=df, aes(xintercept=0), color = "black",
             linetype="dashed")+
  geom_text(mapping=aes(x=-0.35, y=0.75, label="Sacrifice"), size=4, vjust=1.2, hjust=0) +
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.3, end=0.9)+
  geom_text(mapping=aes(x=0.15, y=0.75, label="Gain"), size=4, vjust=1.2, hjust=0) +
  xlab("Valence sacrifice/gain")+
  ylab("Data Density")+
  ggtitle("Participants' preference for valence gain")

ggplot(df, aes(volume_gain, color = "orange"))+
  geom_density(fill = "orange", alpha = 0.2)+
  theme_classic()+
  geom_vline(data=df, aes(xintercept=0), color = "black",
             linetype="dashed")+
  geom_text(mapping=aes(x=-50, y=0.03, label="Sacrifice"), size=3, vjust=1.2, hjust=0) +
  geom_text(mapping=aes(x=35, y=0.03, label="Gain"), size=3, vjust=1.2, hjust=0) +
  xlab("Volume sacrifice/gain")+
  ylab("Data Density")+
  ggtitle("Participants' preference for volume gain")


ggplot(df, aes(volume_diff, color = df$preference))+
  geom_bar(width = 0.1, fill = "white")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.3, end=0.9)+
  #xlab("Emphasis on rating")+
  #ylab("Number of answers")+
  #scale_y_continuous(labels = function(x) format(x/20), limits = c(0,600))+
  #coord_fixed(ratio = 0.007)+
  #theme(legend.position = "none")+
  #theme(axis.text.x = element_text(angle = 50, hjust = 1))+
  ggtitle("Preference depending on volume diff (x axis) and rating diff (facet)")+
  facet_wrap(~valence_diff)




ggplot(df, aes(valence_diff, color = df$preference))+
  geom_bar(width = 0.1, fill = "white")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.3, end=0.9)+
  xlab("Presented difference in valence")+
  ylab("Number of answers")+
  #scale_y_continuous(labels = function(x) format(x/20), limits = c(0,600))+
  #coord_fixed(ratio = 0.007)+
  #theme(legend.position = "none")+
  #theme(axis.text.x = element_text(angle = 50, hjust = 1))+
  ggtitle("Preference depending on difference in valence and volume")+
  facet_wrap(~volume_diff, labeller = label_both)+
  theme(strip.background = element_rect(color="grey", fill="white", size=1.5))+
  labs(color = "Preference")


ggplot(df, aes(rating_opinion, color = df$preference))+
  geom_bar(width = 0.1, fill = "white")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.3, end=0.9)+
  #xlab("Presented difference in valence")+
  #ylab("Number of answers")+
  #scale_y_continuous(labels = function(x) format(x/20), limits = c(0,600))+
  #coord_fixed(ratio = 0.007)+
  #theme(legend.position = "none")+
  #theme(axis.text.x = element_text(angle = 50, hjust = 1))+
  #ggtitle("Preference depending on difference in valence and volume")+
  #facet_wrap(~volume_diff, labeller = label_both)+
  #theme(strip.background = element_rect(color="grey", fill="white", size=1.5))+
   labs(color = "Preference")

#######Participants opinions

ggplot(df, aes(df$rating_opinion, color = df$rating_opinion))+
  geom_bar(width = 0.7, fill = "white")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.3, end=0.9,direction = -1)+
  xlab("Emphasis on rating")+
  ylab("Number of answers")+
  scale_y_continuous(labels = function(x) format(x/20), limits = c(0,600))+
  coord_fixed(ratio = 0.007)+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 50, hjust = 1))+
  ggtitle("Self-evaluated importance of rating")


#add an empty level to volume
df$volume_opinion2 <- factor(df$volume_opinion, levels = c("Not at all", levels(df$volume_opinion)))

ggplot(df, aes(df$volume_opinion, color = df$volume_opinion))+
  geom_bar(width = 0.7, fill = "white")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.3, end=0.75,direction = -1, drop = FALSE)+
  xlab("Emphasis on volume")+
  ylab("Number of answers")+
  scale_y_continuous(labels = function(x) format(x/20), limits = c(0,600))+
  scale_x_discrete(drop = FALSE)+
  coord_fixed(ratio = 0.007)+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 50, hjust = 1))+
  ggtitle("Self-evaluated importance of volume")

ggplot(df, aes(df$content_opinion, color = df$content_opinion))+
  geom_bar(width = 0.7, fill = "white")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.3, end=0.9,direction = -1)+
  xlab("Emphasis on content")+
  ylab("Number of answers")+
  scale_y_continuous(labels = function(x) format(x/20), limits = c(0,600))+
  coord_fixed(ratio = 0.007)+
  theme(legend.position = "none")+
  theme(axis.text.x = element_text(angle = 50, hjust = 1))+
  ggtitle("Self-evaluated importance of content")



opinions_df <-  df %>% 
  select(Participant_ID, rating_opinion, volume_opinion, content_opinion)
  
opinions_df <- opinions_df %>% 
  dplyr::distinct()

opinions_df <-  gather(opinions_df, key = Aspect, value = Opinion, rating_opinion, volume_opinion, content_opinion, factor_key = FALSE)


opinions_df$Aspect <-  as.factor(opinions_df$Aspect)
levels(opinions_df$Aspect)


opinions_prop <- opinions_df %>% 
  group_by(Aspect, Opinion) %>% 
  summarise(n = n()) %>% 
  mutate(prop = n/sum(n))

ggplot(opinions_prop) + geom_col(aes(Aspect, y = prop)) + geom_text(aes(x = Aspect, 
  y = prop + 0.05, label = round(prop, 2)))

library(scales)
ggplot(opinions_prop, aes(x = Aspect,fill = Opinion)) +
  geom_bar(aes(y = ..prop..),stat = "identity") +
  geom_text(size = 3, position = position_stack(vjust = 0.5))+
  geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -.5) +
  theme_classic()+
  scale_fill_viridis(discrete = TRUE, option = "A", begin = 0.3, end=0.9,direction = -1)+
  xlab("Attribute")+
  ylab("Number of answers")+
  coord_fixed(ratio = 0.07)+
  labs(fill = "Importance in decision making")+
  scale_x_discrete(labels=c("Content", "Rating", "Volume"))+
  #theme(axis.text.x = element_text(hjust = 1))+
  ggtitle("Self-evaluated importance of review attributes")







ggplot(df, aes(volume_diff, valence_gain))+
  geom_boxplot()

ggplot(df, aes(preference, valence_diff))+
  geom_jitter()

ggplot(df, aes(volume_diff, preference, colour = preference))+
  scale_colour_viridis(discrete = TRUE, option = "A", begin = 0.4, end=0.75)+
  geom_jitter()

ggplot(df, aes(preference, fill =volume_diff))+
  geom_area(aes(color = volume_diff), stat = 'count')+
  scale_fill_viridis(discrete = TRUE, option = "A")+
  scale_color_viridis(discrete = TRUE, option = "A")+
  theme_minimal()
  #theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  #ylab("Number of times in top 2")+
  #ggtitle("Number of times classifiers were in top 2 of any of the performance scores
  #        Linear SVC selection")



ggplot(df, aes(volume_diff, preference, color = valence_diff))+
  geom_jitter(size=1)+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.3, end=0.9,direction = -1)+
  theme_classic()+
  xlab("Presented difference in volume")+
  ylab("Preference")+
  scale_y_discrete(labels=c("Higher valence", "Higher volume"))+
  labs(color = "Presented difference in valence")+
  ggtitle("Preference depending on presented difference in volume and valence")
  

#simplify valence diff
df <-  df %>% 
  mutate(valence_diff_e = ifelse(as.numeric(as.character(valence_diff)) > 0.5, "over 0.5", "below 0.5"),
         volume_diff_e = ifelse(as.numeric(as.character(volume_diff)) >= 25  , "over 25", "below 25"))



ggplot(df, aes(volume_diff, preference, color = valence_diff_e))+
  geom_jitter(size=1)+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.3, end=0.9,direction = -1)+
  theme_classic()+
  xlab("Presented difference in volume")+
  ylab("Preference")+
  scale_y_discrete(labels=c("Higher valence", "Higher volume"))+
  labs(color = "Presented difference in valence")+
  ggtitle("Simplified: preference based on difference in volume and valence")

df$chosen_dist <-  as.factor(df$chosen_dist)
df$chosen_dist <-  relevel(df$chosen_dist, ref = "smaller_range")

##### Analysis: distributions
ggplot(df, aes(chosen_dist, color = chosen_dist))+
  geom_bar(fill = "white", width = 0.6)+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.1, end=0.5)+
  xlab("Chosen distribution")+
  ylab("Number of answers")+
  scale_x_discrete(labels=c("Smaller range", "Larger range"))+
  coord_fixed(ratio = 0.004)+
  theme(legend.position = "none")+
  #theme(axis.text.x = element_text(angle = 50, hjust = 1))+
  ggtitle("Participants' preference for distribution type")

ggplot(df, aes(chosen_dist, chosen_valence, color = chosen_dist))+
  geom_violin() +
  geom_count()+
  #geom_bar(width = 0.2, fill = "white", position = "dodge")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.1, end=0.5)+
  scale_x_discrete(labels=c("Smaller range", "Larger range"))+
  xlab("Chosen distribution")+
  ylab("Presented valence")+
  coord_fixed(ratio = 2)+
  ggtitle("Preference for distributions depending on valence")




ggplot(df, aes(chosen_dist, chosen_volume, color = chosen_dist))+
  geom_boxplot() +
  geom_jitter(size = 1, alpha = 0.1)+
  #geom_bar(width = 0.2, fill = "white", position = "dodge")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.1, end=0.5)+
  scale_x_discrete(labels=c("Smaller range", "Larger range"))+
  xlab("Chosen distribution")+
  ylab("Presented volume")+
  coord_fixed(ratio = 0.01)+
  ggtitle("Preference for distributions depending on volume")


ggplot(df, aes(chosen_valence, chosen_dist, color = chosen_dist))+
  geom_boxplot() +
  geom_jitter(size = 1, alpha = 0.1)+
  #geom_bar(width = 0.2, fill = "white", position = "dodge")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.1, end=0.5)+
  scale_x_discrete(labels=c("Smaller range", "Larger range"))+
  xlab("Chosen distribution")+
  ylab("Presented valence")+
  coord_fixed(ratio = 2)+
  ggtitle("Preference for distributions depending on valence")

valence_values <- range(3.7, 4.9, )

ggplot(df, aes(chosen_valence, color = chosen_dist))+
  geom_smooth(method = "lm", stat = "count")+
  #geom_count()+
  #geom_bar(width = 0.2, fill = "white", position = "dodge")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.1, end=0.5)+
  scale_x_continuous(breaks = c(3.7, 3.9,  4.1, 4.3, 4.5, 4.7, 4.9))+
  xlab("Valence of the product")+
  ylab("Data density")+
  #coord_fixed(ratio = 2)+
  labs(color = "Distribution choice")+
  ggtitle("Preference for distributions depending on valence")

ggplot(df, aes(chosen_volume, color = chosen_dist))+
  geom_density( aes(fill = chosen_dist, alpha = 0.5), position = "dodge") +
  #geom_count()+
  #geom_bar(width = 0.2, fill = "white", position = "dodge")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.5, end=0.9)+
  scale_fill_viridis(discrete = TRUE, option = "A",begin = 0.2, end=0.5)+
  #scale_x_discrete(labels=c("Smaller range", "Larger range"))+
  xlab("Volume of reviews for the product")+
  ylab("Data density")+
  ggtitle("Preference for distributions depending on volume")

ggplot(df, aes(chosen_volume, color = preference))+
  geom_density( aes(fill = preference, alpha = 0.5), position = "dodge") +
  #geom_count()+
  #geom_bar(width = 0.2, fill = "white", position = "dodge")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.5, end=0.9)+
  scale_fill_viridis(discrete = TRUE, option = "A",begin = 0.2, end=0.5)+
  #scale_x_discrete(labels=c("Smaller range", "Larger range"))+
  xlab("Volume of reviews for the product")+
  ylab("Data density")+
  ggtitle("Preference for distributions depending on volume")

ggplot(df, aes(chosen_valence, color = preference))+
  geom_density( aes(fill = preference, alpha = 0.5), position = "dodge") +
  #geom_count()+
  #geom_bar(width = 0.2, fill = "white", position = "dodge")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.5, end=0.9)+
  scale_fill_viridis(discrete = TRUE, option = "A",begin = 0.2, end=0.5)+
  #scale_x_discrete(labels=c("Smaller range", "Larger range"))+
  xlab("Volume of reviews for the product")+
  ylab("Data density")+
  ggtitle("Preference for distributions depending on volume")

```



#Statistical Analysis

Modeling and stuff

1.

2. 
```{r}
write_csv(df, "sunday_version_df.csv")

pacman::p_load(lmerTest)

df$preference <- as.factor(df$preference)
levels(df$preference) #we are predicting


m1 <-  glmer(preference ~ valence_diff_e + volume_diff_e +valence_diff_e*volume_diff_e+ (1|Participant_ID) ,family="binomial", df)

summary(m1)
boot::inv.logit(-1.4265)
boot::inv.logit(-1.4265+1.0837)

df$volume_diff_n <- as.numeric(as.character(df$volume_diff))
df$valence_diff_n <- as.numeric(as.character(df$valence_diff))

df$volume_diff_n_s <- df$volume_diff_n - mean(df$volume_diff_n)
df$valence_diff_n_s <- df$valence_diff_n - mean(df$valence_diff_n)



ggplot(df, aes(chosen_volume, color = preference))+
  geom_density( aes(fill = preference, alpha = 0.5), position = "dodge") +
  #geom_count()+
  #geom_bar(width = 0.2, fill = "white", position = "dodge")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A",begin = 0.3, end=0.9)+
  scale_fill_viridis(discrete = TRUE, option = "A",begin = 0.3, end=0.9)+
  #scale_x_discrete(labels=c("Smaller range", "Larger range"))+
  xlab("Volume of reviews for the product")+
  ylab("Data density")+
  ggtitle("Preference for attribute depending on volume")

ggplot(df, aes(chosen_valence, color = preference))+
  geom_density( aes(fill = preference, alpha = 0.5), position = "dodge") +
  #geom_count()+
  #geom_bar(width = 0.2, fill = "white", position = "dodge")+
  theme_classic()+
  scale_color_viridis(discrete = TRUE, option = "A",begin = 0.3, end=0.9)+
  scale_fill_viridis(discrete = TRUE, option = "A",begin = 0.3, end=0.9)+
  #scale_x_discrete(labels=c("Smaller range", "Larger range"))+
  xlab("Product's rating")+
  ylab("Data density")+
  ggtitle("Preference for attribute depending on valence")

######################ACTUAL MODELS ##################################3

#chi squared
df %>% 
  group_by(chosen_dist) %>% 
  summarise(number_times_chosen = n(), prob_in_stimuli = 0.5)

obs <- c(712,408)
exp <- c(.50, 0.50)
chisq.test(obs, p=exp)


#Model 1
levels(df$preference)
m1 <-  glmer(preference ~ valence_diff_n + volume_diff_n +valence_diff_n*volume_diff_n+ (1+ valence_diff_n+volume_diff_n|Participant_ID) ,family="binomial", df)
summary(m1)




m2 <-  glmer(preference ~ valence_diff_n + volume_diff_n +valence_diff_n*volume_diff_n+ (1+ valence_diff_n+volume_diff_n|Participant_ID) ,family="binomial", df)
summary(m2)


ggplot(df, aes(chosen_dist))+
  geom_bar( aes(fill = chosen_dist, alpha = 0.5), position = "identity") +
  #theme_classic()+
  #geom_vline(data=df, aes(xintercept=0), color = "black",linetype="dashed")+
  #geom_text(mapping=aes(x=-0.35, y=0.75, label="Sacrifice"), size=4, vjust=1.2, hjust=0) +
  scale_color_viridis(discrete = TRUE, option = "A", begin = 0.3, end=0.9)+
  #geom_text(mapping=aes(x=0.15, y=0.75, label="Gain"), size=4, vjust=1.2, hjust=0) +
  #xlab("Valence sacrifice/gain")+
  #ylab("Data Density")+
  ggtitle("Participants' preference for valence gain")

ggplot(df, aes(x = chosen_dist)) +
  geom_bar(stat = "count") +
  #geom_text(size = 3, position = position_stack(vjust = 0.5))+
  #geom_text(aes( label = scales::percent(..prop..),y= ..prop.. ), stat= "count", vjust = -.5) +
  theme_classic()+
  scale_fill_viridis(discrete = TRUE, option = "A", begin = 0.3, end=0.9,direction = -1)+
  #xlab("Attribute")+
  #ylab("Number of answers")+
  #coord_fixed(ratio = 0.07)+
  labs(fill = "Importance in decision making")+
  #theme(axis.text.x = element_text(hjust = 1))+
  ggtitle("Self-evaluated importance of review attributes")


```

chisq.test(obs, p=exp)


Null hypothesis: The proportion of smaller and larger distribution is 50% and 50%, respectively.
Alternative hypothesis: At least one of the proportions in the null hypothesis is false.

If the P-value is less than the significance level (0.05), we cannot accept the null hypothesis.
If the P-value is above 0.05, we can accept the null hypothesis 

Model 2: Choice of distribution = ð›¼p + ð›½p âˆ— Valence + Æ
Model 3: Choice of distribution = ð›¼p + ð›½p âˆ— Volume + Æ

```{r}
#Model 1
levels(df$preference)
m1 <-  glmer(preference ~ valence_diff_n + (1+ valence_diff_n|Participant_ID) ,family="binomial", df)
summary(m1)

m2 <-  glmer(preference ~ volume_diff_n + (1+ volume_diff_n|Participant_ID) ,family="binomial", df)
summary(m2)

m3 <-  glmer(preference ~ valence_diff_n + volume_diff_n +valence_diff_n*volume_diff_n+ (1+ valence_diff_n+volume_diff_n|Participant_ID) ,family="binomial", df)
summary(m3)

m4 <- glmer(chosen_dist ~ chosen_valence + (1+ chosen_valence|Participant_ID) ,family="binomial", df)
summary(m4)

m5 <-  glmer(chosen_dist ~ chosen_volume+ (1+ chosen_volume|Participant_ID) ,family="binomial", df)
summary(m5)
```


